Single Cell Xenopus TMT Analysis

### 2020-03-05 Manuscript/Manuscript.Rmd
updated

library(knitr)
library(tidyverse)
library(RColorBrewer)
library(pheatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)
library(cowplot)
library(patchwork)
source("../functions.R")
library(knitcitations)

@@

```{r figure_1, echo=FALSE, fig.height=6.5, fig.width=6.5, message=FALSE, warning=FALSE, fig.cap=fig_legend_1}

@@

p1 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = time, y = abundance, color = protein)) + geom_path() +
  facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")

p2 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = protein, y = abundance, color = protein)) + 
  geom_boxplot() + facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")

p3 <- rbind(low_cor, high_cor) %>%
  ggplot(., aes(x = ProtA, y = ProtB, color = cor)) + geom_point() +
  stat_ellipse() +
  theme_minimal() +
  theme(legend.position = "bottom")

p4 <- tibble(cor = c("High Cor","Low Cor"),
       var_sum = c(sqrt(30^2 + 30^2 + 2*0.8*30^2),
                   sqrt(30^2 + 30^2 + 2*0*30^2))) %>%
  ggplot(., aes(x = cor, y = var_sum, fill = cor)) + geom_bar(stat = "identity") +
  theme_minimal()

@@

p1 / (p3 + p4) + plot_annotation(tag_levels = "A") & theme(legend.position = "none")

fig_legend_1 <- c("A) Simulated expression of two proteins over time in a single cell with a mean of 100 and a standard deviation of 30 with expression correlations of 0 and 0.8. B) Pairwise plots of the two proteins in the single cells between uncorrelated and correlated scenerios. C) The total variance between the uncorrelated and correlated scenerios from A and B.")

>>>>

library(knitr)
library(tidyverse)
library(RColorBrewer)
#library(pheatmap)
library(ComplexHeatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)
library(cowplot)
library(patchwork)
source("../functions.R")
library(knitcitations)
library(ggplotify)

@@

```{r figure_1, echo=FALSE, fig.height=8, fig.width=6, message=FALSE, warning=FALSE, fig.cap=fig_legend_1}

@@

p1 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = time, y = abundance, color = protein)) + geom_path() +
  facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "none")

p2 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = protein, y = abundance, color = protein)) + 
  geom_boxplot() + facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "none")

p3 <- rbind(low_cor, high_cor) %>%
  ggplot(., aes(x = ProtA, y = ProtB, color = cor)) + geom_point() +
  stat_ellipse() +
  theme_minimal() +
  theme(legend.position = "none")

p4 <- tibble(cor = c("High Cor","Low Cor"),
       var_sum = c(sqrt(30^2 + 30^2 + 2*0.8*30^2),
                   sqrt(30^2 + 30^2 + 2*0*30^2))) %>%
  ggplot(., aes(x = cor, y = var_sum, fill = cor)) + geom_bar(stat = "identity") +
  theme_minimal() +
  theme(legend.position = "none")

# Variation histogram
p5 <- ggplot(protVar, aes(x = cv)) + 
  geom_histogram(bins = 200) + xlim(0,.8) + theme_minimal() +
  theme(legend.position = "none")

# Correlation matrix
cor = cor(t(log2(protImpute[c(1:ncol(protImpute))[-c(1,grep('ctrl',colnames(protImpute)))]])), use = 'pairwise.complete.obs')
colnames(cor) = protImpute$Uniprot
rownames(cor) = protImpute$Uniprot

mypal = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201))

p6 <- as.ggplot(
  Heatmap(cor, 
        col = mypal,
        heatmap_legend_param = list(title = "R"),
        show_column_dend = FALSE,
        show_row_dend = FALSE,
        show_column_names = FALSE,
        show_row_names = FALSE,
        use_raster = TRUE,
        raster_quality = 1)
  )

@@

(p1 / (p3 + p4)) / (p5 + p6) + 
  plot_annotation(tag_levels = "A")

fig_legend_1 <- c("A) Simulated expression of two proteins over time in a single cell with a mean of 100 and a standard deviation of 30 with expression correlations of 0 and 0.8. B) Pairwise plots of the two proteins in the single cells between uncorrelated and correlated scenerios. C) The total variance between the uncorrelated and correlated scenerios from A and B. D) Histogram of the coefficient of variation of all measured proteins. E) Heatmap of the pairwise correlation coefficients between all measured protein pairs.")

### 2020-03-05 Untitled.Rmd
updated

## Plots
```{r fig.height=8, fig.width=5}
allGO1 <- allGO1 %>% mutate(interval = cut_number(normVar, n = 10))

ggplot(allGO1, aes(x = normVar)) + geom_histogram(bins = 50)

ggplot(allGO1, 
       aes(x = medCors, y = medCV, color = interval == "[0.00652,0.0333]")) + 
  geom_point(alpha = 0.5) + theme_bw() +
  #facet_wrap(~interval) +
  theme(legend.position = "bottom")

ggplot(allGO1, 
       aes(x = medCors, y = medCV)) + 
  geom_point(alpha = 0.5) + theme_bw() +
  geom_label_repel(data = filter(allGO1, 
                                 interval == "[0.00652,0.0333]",
                                 medCors > 0.15), 
                  aes(label = GO), 
                  colour = 'black', 
                  size = 2,
                  force = 10) + 
  theme_bw()
```

@@

>>>>

## Plots
```{r}
allGO1 <- allGO1 %>% mutate(interval = cut_number(normVar, n = 10))

ggplot(allGO1, aes(x = normVar)) + geom_histogram(bins = 100, aes(fill = interval))

ggplot(allGO1, 
       aes(x = medCors, y = medCV, color = interval)) + 
  geom_point(alpha = 0.5) + theme_bw() +
  #facet_wrap(~interval) +
  theme(legend.position = "bottom")

ggplot(allGO1, 
       aes(x = medCors, y = medCV)) + 
  geom_point(alpha = 0.5) + theme_bw() +
  geom_label_repel(data = filter(allGO1, 
                                 interval == "[0.142,0.38]",
                                 medCors > 0.15), 
                  aes(label = GO), 
                  colour = 'black', 
                  size = 2,
                  force = 10) + 
  theme_bw()
```

@@

n <- 2
R <- 0.8

model_tot_var <- function(n,R,v){
  sqrt(n*v^2 + n*2*R*v^2)
}
